%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Adrin} % Your first name
\familyname{Jalali} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Greifenhagener Str. 9}{10437, Berlin, Germany}
\mobile{+49-151-68121562}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{adrin.jalali@gmail.com}
\homepage{github.com/adrinjalali}{github/adrinjalali}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%\section{Objective}
%\cvitem{}{To dedicate my time, experience and expertise in machine learning, algorithms, and programming, to projects that matter to people's well-being.}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
\cventry{2016-Present}{MisterSpex GmbH}{Business Intelligence Department}{Berlin, Germany}{}{
  \begin{itemize}
  \item  Dynamic ordering of products on landing pages based on several KPIs - \textbf{R, TSQL}
  \item  Improving Google AdWords ad placement and bidding strategies - \textbf{Python}
  \end{itemize}
  }

%\subsection{Research Positions}
\cventry{2012-Present}{Max Planck Institute for Informatics}{Computational Biology and Applied Algorithmics Department}{Saarbr\"ucken, Germany}{}{
\begin{itemize}
\item Interpretable Sparse methods for cancer associations using an ensemble of sparse support vector machines (SVMs) - \textbf{Python}
%\begin{itemize}
%\item Interpretable per Case Weighted Ensemble Method for Cancer Associations: unlike conventional ensemble methods, in this work we introduced a weighting mechanism for the voting process over individual learners which adapts to each given test sample in order to compensate for the batch effects and noise in the data~[2].
  %The \href{https://github.com/adrinjalali/Network-Classifier/tree/devel}{Code}, an \href{http://link.springer.com/chapter/10.1007/978-3-662-44753-6_26}{extended abstract[2]}, and a \href{http://biorxiv.org/content/early/2014/09/15/008185}{pre-print} of the work are available.
%\end{itemize}
\end{itemize}}

\cventry{2011-2012}{British Columbia Cancer Research Center}{Terry Fox Laboratory}{Vancouver, Canada}{}{
\begin{itemize}
\item Automated flow cytometry data analysis and visualization using dynamic programming, clustering, graph algorithms, and SVMs  - \textbf{C++, R}
%\begin{itemize}
%\item Cellular hierarchy optimization for flow cytometry~[3, 4]
  %: Problem was modelled onto a graph and finding k-shortest paths
%in that graph was equivalent to having the solution. \href{http://cran.r-project.org/web/packages/kBestShortestPaths/index.html}{kBestShortestPaths} in CRAN, \href{http://www.bioconductor.org/packages/release/bioc/html/RchyOptimyx.html}{RchyOptimyx} in Bioconductor, and two publications [\href{http://onlinelibrary.wiley.com/doi/10.1002/cyto.a.22209/full}{3}, \href{http://bioinformatics.oxfordjournals.org/content/30/9/1329.short}{4}] are available as a result of the study.
%\item Classification of samples into diffuse large B-cell lymphoma and follicular lymphoma using flow cytometry experiments
  %: Features were extracted using clustering
%as the input of a bootstrap, feature selection, and classifier pipeline.
%\item Search for chemotherapy resistant cell populations using pre- and post-therapy flow cytometry experiments
  %: RchyOptimyx pipeline was used to find
%cell populations with high enrichment factors, \emph{i.e.} enriched cell populations after therapy that were resistant to chemotherapy.
%\item Characterization of heterogeneity in chronic lymphocytic leukemia
  %: Patient samples are clustered into different groups according to their cell populations and important cell populations in differentiating those clusters are identified.
%\end{itemize}
\end{itemize}}

%\subsection{Professional Employment}
\cventry{2009--2011}{Tosan Intelligent Data Miners}{R\&D Department}{Tehran, Iran}{}{
%\newline{}\newline{}
\begin{itemize}
\item Fraud detection in banks, \emph{Project Manager} - \textbf{C++, Java, Oracle, Microsoft BI}
  \begin{itemize}
  \item Behavioral clustering of bank employees in time to detect major behavioral changes as anomalies.
  \item Behavioral clustering of customers according to their debit card transactions in time to detect changes as potential fraud.
  \end{itemize}
\item Operational intelligence, \emph{Project Manager} - \textbf{C++, Oracle, MATLAB, Java}
  \begin{itemize}
  \item Predict the terminal type of the next transaction of the customers using their transaction history.
  \item Soft cluster customers according to their fuzzified transaction times and detect abnormal changes in cluster membership values.
  \item Build a graph model to predict geographical location of terminals using customers' transaction history.
  \end{itemize}
\end{itemize}}

\cventry{2008}{Orado Group}{}{Tehran, Iran}{}{
Programmer in an educational/social network targeting Iranian secondary and high school students - \textbf{C\#, T-SQL}}

\cventry{2006--2007}{Fidofa Software Group}{}{Tehran, Iran}{}{
\begin{itemize}
\item Automatic trading system in futures stock market, \emph{Programmer} - \textbf{Matlab, C\#}
\begin{itemize}
\item Implementation of Markowitz modern portfolio theory.
\item Implementation of GARCH indicator for stock market price.
\item Optimize parameters of company's existing trading systems using a genetic algorithm.
\end{itemize}
\end{itemize}}

\cventry{2006}{Sourena Software Group}{}{Tehran, Iran}{}{
Programmer in a Persian text to speech project - \textbf{C\#}}

\cventry{2005}{Tarrah Sarv System}{}{Tehran, Iran}{}{
Programmer in a system handling all personnel and factory processes of a chicken farm - \textbf{Delphi, T-SQL}}

%\clearpage
\subsection{Other Experience}

\cventry{2009}{University of Tehran}{Mining Department}{Tehran, Iran}{}{
  Predicting Compressional and Shear Wave Velocities in dam sites in south west of Iran having
sparse samples taken from the site before construction of dams using an adaptive Neuro-Fuzzy Inference System model - \textbf{Matlab}}

\cventry{2006}{University of Tehran}{Management Faculty}{Tehran, Iran}{}{
  Semi-dynamic recommendation system for semi-dynamic retail store/ad-based websites using singular value decomposition and a genetic
  algorithm - \textbf{C++}}
%We developed a system to allow websites to have multiple structures to target different user groups according to their click-stream
%and product ratings. The system constructs structures offline, and later on these structures can be uploaded to be shown
%to users according to their behavior. The project targets websites that cannot afford the computational intensive processes
%of having a fully dynamic website. We designed a
%system including a singular value decomposition (SVD) method to fill in the rating missing values, as well as a genetic algorithm
%to find multiple website structures.}

\cventry{2005}{Tehran Polytechnic}{Computer Engineering Department}{Tehran, Iran}{}{
  Power efficient semi-random message passing and routing algorithm for ad-hoc mobile sensor networks - \textbf{C++}}
%OMNet++

\cventry{2002--2005}{Tehran Polytechnic}{Rescue Simulation League, Robotics Lab}{Tehran, Iran}{}{
  \begin{itemize}
  \item[] \emph{7th place, world cup 2002 Italy}
  \item[] \emph{5th place, world cup 2005 Japan}
  \item[] Fire brigades and police forces - \textbf{C++}
    \begin{itemize}
    \item Clustering of the buildings of the simulated world using self organizing map.
    \item Program a strategy accordingly to find the best order of the buildings to be extinguished by fire brigades.
    \end{itemize}
  \end{itemize}
}

\subsection{Teaching Positions}
\cventry {2011}{Lecturer}{Introduction to Programming}{Department of Fundamental Sciences}{University of Tehran, Tehran, Iran}{}
\cventry {2006}{Teaching Assistant}{Introduction to Graphics Programming in C}{Department of Mechanical, Civil, and Texture Engineering}{Tehran Polytechnic, Tehran, Iran}{}
\cventry {2006}{Teaching Assistant}{Data Structures and Algorithms}{Department of Math and Computer Science}{Tehran Polytechnic, Tehran, Iran}{}
\cventry {2005}{Teaching Assistant}{Compilers}{Department of Math and Computer Science}{Tehran Polytechnic, Tehran, Iran}{}
\cventry {2004}{Teaching Assistant}{Micro Processors}{Department of Math and Computer Science}{Tehran Polytechnic, Tehran, Iran}{}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\section{Education}

\cventry{2012--Present}{PhD (cont.) in Computer Science/Bioinformatics}{Max Planck Institute for Informatics, Computational Biology and Applied Algorithmics Department}{Saarbr\"ucken, Germany}{\newline{}\emph{Supervisors:} Dr. Nico Pfeifer, Prof. Dr. Dr. Thomas Lengauer,\newline{}\emph{Dissertation Topic:} Machine Learning in Cancer Diagnosis,\newline{}\emph{Degree anticipated:} July 2016}{}
\cventry{2011--2012}{PhD in Bioinformatics}{University of British Columbia, British Columbia Cancer Research Center, Terry Fox Laboratory}{Vancouver, Canada}{\newline{}\emph{Supervisor:} Dr. Ryan Brinkman,\newline{}\emph{Topic:} Automated analysis of flow-cytometry data}{}
\cventry{2006--2009}{MSc in Computer Science}{University of Tehran, School of Mathematics, Statistics, and Computer Science}{Tehran, Iran}{\newline{}\emph{Supervisor:} Dr. Abbas Nowzari-Dalini,\newline{}\emph{Thesis Topic:} Finding DNA Motifs Using Bidirectional Recurrent Neural Networks,\newline{}\emph{GPA:} 18.42/20}{}
\cventry{2002--2006}{BSc in Computer Science}{Tehran Polytechnic, Department of Mathematics, and Computer Science}{Tehran, Iran}{\newline{}\emph{Thesis Topic:} Design and Implementation of a Genetic Algorithm to Solve Time Table of a School,\newline{}\emph{GPA:} 15.98/20}{}

\section{Service}
\cventry{2015}{Chemistry, Physics, and Technology Section Representative}{\href{http://www.phdnet.mpg.de/cms/}{PhDnet} steering group}{Max Planck Society}{Germany}{}
\cventry{2012}{Bioinformatics Representative}{College for Interdisciplinary Studies Graduate Student Society}{University of British Columbia}{Vancouver, Canada}{}
\cventry{2012}{``Bioinformatics'' and \href{http://www.graspods.com/}{``British Columbia Cancer Agency Graduate Student and Post Doctoral Fellow Society''} representative}{\href{http://gss.ubc.ca/main/}{Graduate Student Society}}{University of British Columbia}{Vancouver, Canada}{}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer Skills}

\cvitem{}{\textbf{C, C++, Python, Linux}}
\cvitem{}{C\#, Java, R, Matlab, T-SQL, PL/SQL}
\cvitem{}{Oracle, MySql, MS-SQLServer, SSAS}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Persian}{Native}{}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{German}{Intermediate ($\sim$B1)}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

%\cvlistdoubleitem{Biking}{Karate}
%\cvlistdoubleitem{Reading}{Movies}

\section{Publications}

\begin{enumerate}
\item Jalali A., and Pfeifer N., \emph{Interpretable per Case Weighted Ensemble Method for Cancer Associations}, BMC Genomics, volume 17, no. 1, 2016.

\item Courtot M., Meskas J., Diehl A. D., Droumeva R., Gottardo R., Jalali A., Taghiyar M.J., \emph{flowCL: ontology-based cell population labelling in flow cytometry}, Bioinformatics 31, no. 8 (2015): 1337-1339.

\item Jalali A., and Pfeifer N., \emph{Interpretable per Case Weighted Ensemble Method for Cancer Associations}, Algorithms in Bioinformatics, pp. 352-353. Springer Berlin Heidelberg, 2014.

\item O'Neill K.*, Jalali A.*, Aghaeepour N.*, Hoos H.H., and Brinkman R.R., \emph{Enhanced flowType/RchyOptimyx: A Bioconductor pipeline for discovery in high-dimensional cytometry data}, Bioinformatics (2014), doi: 10.1093/bioinformatics/btt770.

\item Jalali A.*, Aghaeepour N.*, O'Neill K., Chattopadhyay P.K., Roederer M., Hoos H.H., Brinkman R.R., \emph{RchyOptimyx: cellular hierarchy optimization for flow cytometry}, Cytometry Part A 81, no. 12 (2012): 1022-1030.

\item Aghaeepour N., Chattopadhyay P.K., Ganesan A., O'Neill K., Zare H., Jalali A., Hoos H.H., Roederer M., and Brinkman R.R., \emph{Early Immunologic Correlates of HIV Protection can be Identiﬁed from Computational Analysis of Complex Multivariate T-cell Flow Cytometry Assays},
Bioinformatics, 2012: 28(7):1009–1016.

\item Rezaei F.*, Jalali A.*, Memarian H., \emph{Estimation of Compressional and Shear Wave Velocities using Adaptive Neuro-Fuzzy Inference System, in some of dam sites in south west of Iran}, Journal of the Earth, Tehran, Iran, 2009.

\item Behsaz B., Jalali A., Janzadeh H., Jouyandeh M.R.., Molazem F., Rahimi A., Salehi A., and Tavakoli Ghinani M., \emph{Team Description of S.O.S. 2005}, Proceedings CD RoboCup 2005, Osaka, Japan, 2005.
  
\item Tashakori M., Jalali A., Jooyandeh M.R., Gholami A., Behzadian A., Ghasemloo K., Esfahbod B., \emph{Rayan Team Strategy Description}, Proceedings CD RoboCup 2004, Lisboa, Portugal, 2004.
  
\item Shiri M.E., Jalali A., Jooyandeh M.R., Roshandel Tavana R., Behzadi M., \emph{AUTRescue Team Strategy Description}, Proceedings CD RoboCup 2003, Springer-Verlag, Padova, Italy, 2003. 
\end{enumerate}

\vspace{.5cm}
\small{* co-authors contributed equally}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\recipient{$ $}{$ $}
%\date{\today} % Letter date
%\opening{Dear Madam/Sir,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%Hereby I'd like to apply for your ``Software Developer C++/Java'' position. Currently I'm writing my PhD thesis in Saarbr\"ucken and expect to hand it in by the end of this year. Therefore I will be available from January 2016.

%My experience with Oracle dates back to Oracle 8. Since then, until I started my PhD in 2011, I've been involved with several projects as back-end developer and/or database designer.

%One of my favorite projects was an SMS gateway, when the SLA of a contract was 15000 SMS/second and the system could handle only 5000 SMS/second at the time. We found its bottleneck, tweaked the system's architecture, and after a week it delivered the desired SLA.

%Another longer term project was in 2010-2011 when we where handling bank transactions for the operational intelligence project in \emph{Kishware Software Group}. The load was 15 million a day on its peak, and our statistical analysis had 10ms for each transaction to return its estimated risk. We developed our core in C++ and used Oracle for our offline storage and analysis, and server's main memory for the real-time analysis. MATLAB and Weka (in Java) were our machine learning analysis tools. I started as a researcher in that team and ended up as its project manager.

%During my PhD I've used R and Python to analyze our data. I also gained statistical machine learning knowledge as a part of my training and during the projects I've been doing. I'm also a part-time system administrator in a department at the Saarland University, and I handle their servers which include: virtual machines, a compute cluster, and GPU servers, as well as their infrastructure servers such as Kerberos/LDAP, mail server, git server (gitlab), etc.

%Consequently, the job description lists many skills that I feel confident in them, alongside some other skills that I would enjoy learning them. I'm really excited about the position, and I hope I can be a good member of you team.

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}
